Supplementary Report for the article *Functional diversity can facilitate the collapse of an undesirable ecosystem state*

### 2022-09-28 experiments/2_supplement/supplement.Rmd
update figures

(ref:max-tol1) Effects of strain variation on position of tipping points compared between simulations with all (nine) strains present and simulations where only the most tolerant strain is present.

@@

@@

```{r max-tol2, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol2)', fig.height=10, fig.width=8, fig.align="center"}
## max SB_var_gmax_s is 0.09473684
nine_strain_one <- filter(nine_strains,
       CB_var_gmax_s == 0,
       abs(SB_var_gmax_s - 0.09473684) < 0.001,
       PB_var_gmax_s == 0)
fig_state_vs_o2diff_sidebyside_alternative(nine_strain_one)
```

@@

```{r max-tol3, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol3)', fig.height=10, fig.width=8, fig.align="center"}
max_tol_one <- filter(maxtolonly_strains,
       CB_var_gmax_s == 0,
       abs(SB_var_gmax_s - 0.09473684) < 0.001,
       PB_var_gmax_s == 0)
fig_state_vs_o2diff_sidebyside_alternative(max_tol_one)
```

@@

```{r max-tol4, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol4)', fig.height=10, fig.width=8, fig.align="center"}
filter(nine_strains,
       abs(CB_var_gmax_s - 0.026592798) < 0.001,
       abs(SB_var_gmax_s - 0.079778395) < 0.001,
       PB_var_gmax_s == 0) %>%
  fig_state_vs_o2diff_sidebyside_alternative()
```

@@

```{r max-tol5, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol5)', fig.height=10, fig.width=8, fig.align="center"}
max_tol_one_CBSB <- filter(maxtolonly_strains,
       abs(CB_var_gmax_s - 0.026592798) < 0.001,
       abs(SB_var_gmax_s - 0.079778395) < 0.001,
       PB_var_gmax_s == 0)
fig_state_vs_o2diff_sidebyside_alternative(max_tol_one_CBSB)
```

>>>>

(ref:max-tol1) Effects of strain variation on position of tipping points compared between simulations with all (nine) strains present and simulations where only the most tolerant strain is present. In the SB and CB-SB treatments there is missing data in the case with only the most tolerant strain when there were no alternate stable states and therefore no tipping points.

@@

## remove data where there are no stable states
## this subset is identified by inspection of the figure
all_stab <- all_stab %>%
  filter(!(var_treat == "SB" & stand_var > 0.88 & num_strains == -1),
         !(var_treat == "CB-SB" & stand_var > 0.84 & num_strains == -1))

@@

```{r max-tol2, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol2)', fig.height=10, fig.width=8, fig.align="center"}
## max SB_var_gmax_s is 0.09473684
nine_strain_one <- filter(nine_strains,
       CB_var_gmax_s == 0,
       abs(SB_var_gmax_s - 0.09473684) < 0.001,
       PB_var_gmax_s == 0)
ss_result <- nine_strain_one
fig_state_vs_o2diff_sidebyside_alternative_leftfliponly(nine_strain_one)
```

@@

```{r max-tol3, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol3)', fig.height=10, fig.width=8, fig.align="center"}
max_tol_one <- filter(maxtolonly_strains,
       CB_var_gmax_s == 0,
       abs(SB_var_gmax_s - 0.09473684) < 0.001,
       PB_var_gmax_s == 0)
fig_state_vs_o2diff_sidebyside_alternative_nofliparrows(max_tol_one)
```

@@

```{r max-tol4, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol4)', fig.height=10, fig.width=8, fig.align="center"}
filter(nine_strains,
       abs(CB_var_gmax_s - 0.026592798) < 0.001,
       abs(SB_var_gmax_s - 0.079778395) < 0.001,
       PB_var_gmax_s == 0) %>%
fig_state_vs_o2diff_sidebyside_alternative_leftfliponly()
```

@@

```{r max-tol5, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol5)', fig.height=10, fig.width=8, fig.align="center"}
max_tol_one_CBSB <- filter(maxtolonly_strains,
       abs(CB_var_gmax_s - 0.026592798) < 0.001,
       abs(SB_var_gmax_s - 0.079778395) < 0.001,
       PB_var_gmax_s == 0)
fig_state_vs_o2diff_sidebyside_alternative_nofliparrows(max_tol_one_CBSB)
```
